---
title: "Analysis report"
author: "Luke Maurits"
date: '`r Sys.Date()`'
output: pdf_document
---

```{r setup, include=FALSE}
library(tidyverse)
knitr::opts_chunk$set(echo = TRUE)
my_demogs <- read_csv("data/demogs.csv")
my_data <- read_csv("data/processed_data.csv")
m <- read_rds("fitted_model.rds")
```

## Raw data summary

### Participants

We collected data from `r length(unique(my_data$ID))` children,
`r sum(my_demogs$gender=="F")` females and
`r sum(my_demogs$gender=="M")` males.  Ages ranged from
`r min(my_demogs$age)` to `r max(my_demogs$age)`, with a mean age of
`r round(mean(my_demogs$age),2)` (SD `r round(sd(my_demogs$age),2)`).

### Response rates

Response counts and rates per condition:

```{r}
my_data %>%
  group_by(condition) %>%
  summarise(count=sum(response), rate = mean(response))
```


### Response times

Mean response times per condition:
```{r}
my_data %>%
  group_by(condition) %>%
  summarise(mean_rt = mean(latency))
```

## Logistic regression

### Model summary

```{r}
summary(m)
```

### Visualising model predictions

```{r}
my_plot <- my_data %>%
  mutate(predictions = predict(m, type="response")) %>%
  ggplot() +
  geom_line(aes(x=age, y=predictions, colour=condition, linetype=gender)) +
  geom_jitter(aes(x=age, y=response, colour=condition, shape=gender), height=0.05, width=0.2)
ggsave("plots/model_predictions.png", my_plot, create.dir = TRUE)
my_plot
```